XOR power analysis

### 2021-08-26 analysis/xor-some_power.Rmd
add models with main effect of SI trigger

isSingular(model_some)
summary(model_some)
```

>>>>

isSingular(model_some)
summary(model_some)
```
### Explore model with main effect of SI trigger
```{r, results='hide'}
# Full model 
# sum-code effect of SI trigger
d_both <- d_both %>% mutate(
  main_type = as.factor(main_type)
)
# some = 1, xor = -1
contrasts(d_both$main_type) <- contr.sum(2)
# try to fit maximal model with brm
model_SI_brm <- brms::brm(target ~ prior*competence*relevance* main_type +
                   (1 + prior + competence + relevance + main_type || submission_id) +
                   (1 | title),
                 data = d_both,
                 control = list(adapt_delta = 0.95),
                 cores = 4,
                 iter = 2000)
```
```{r}
summary(model_SI_brm)
```

```{r, results='hide'}
## frequentist model for observed power exploration
# does not converge with 4-way interaction
model_SI <- lmer(target ~ prior*competence*relevance + main_type +
                   (1 + prior + competence + relevance + main_type | submission_id) +
                   (1 | title),
                 data = d_both
                 )
summary(model_SI)
# also try model with by-subj intercept only for post-hoc power
model_SI_simple <- lmer(target ~ prior*competence*relevance*main_type +
                   (1 | submission_id) +
                   (1 | title),
                 data = d_both
                 )
summary(model_SI_simple)
```
```{r, results='hide', warning=FALSE, message=FALSE}
# check observed power for simple effect of trigger
p_main_type <- powerSim(model_SI_simple, 
                  fixed("main_type1", "z"), 
                  progress = FALSE)
```

```{r}
p_main_type
```
